A meta-analysis of powdery mildew yield loss mitigation strategies in Australian mungbean

### 2020-06-22 03_Prep_data.Rmd
remove warning suppression on code chunk
Markdown syntax, delete chunk that said "delete me"

### Cluster fungicide applications  
We are going to define 'fungicide application timing' as a categorical variable, relative to the first sign of powdery mildew.

These categorical variables are named:  
   - **Early**: First fungicide application was prior to first sign of disease.  
   - **Recommended**: First fungicide application was applied on the day powdery mildew was observed, or within three days of first sign.  
   - **Late**: First fungicide application was four or more days after first sign of disease being observed.

@@

Single sprays of either:  
   a) early,  
   b) recommended timing,  
   c) late.

Two or more sprays where the first spray was either:  
   d) early,  
   e) recommended timing,  
   f) late.

@@

```{r simpler_clusters_remove}
slimmer_PM_dat <-
   slim_PM_dat[slim_PM_dat$spray_management != "Early_plus", ]

@@

```{r dose_lmer}

m1 <-
   lmer(log(grain_yield.t.ha * 1000) ~ factor(spray_management) +
           (1 | trial),
        data = slimmer_PM_dat)

@@

anova(m1,m2)

@@

```{r}
slimmer_PM_dat$trial <- slimmer_PM_dat$trial_noDose
slimmer_PM_dat <- slimmer_PM_dat[,colnames(slimmer_PM_dat) != "trial_noDose"] #remove second trial column
write.csv(slimmer_PM_dat, file = "cache/slimmer_PM_clusterdat.csv", row.names = FALSE)
```

@@

for(i in unique(slimmer_PM_dat$trial_ref)) {
   if (is.na(Trial_Dpress[Trial_Dpress$trial_ref == i, "AUDPC_C"])) {
      next()
   }

@@

   }
}

@@

We may want to consider row spacing in the trials, However one of the locations has NA as the row spacing. 
For now let's assign the most used row spacing of 0.33 m.

```{r}
slimmer_PM_dat[is.na(slimmer_PM_dat$row_spacing),]
slimmer_PM_dat[is.na(slimmer_PM_dat$row_spacing),"row_spacing"] <- 0.33

@@

```{r delete_this_chunk, eval=FALSE, include=FALSE}
PM_MB_means$infected_days <- as.numeric(PM_MB_means$harvest_date - PM_MB_means$first_sign_disease)

plot(AUDPC_m ~ infected_days, data = PM_MB_means)
plot(grain_yield.t.ha. ~ infected_days, data = PM_MB_means)

PM_MB_means$harvest_date - PM_MB_means$first_sign_disease
```

>>>>

### Cluster fungicide applications

We are going to define 'fungicide application timing' as a categorical variable, relative to the first sign of powdery mildew.

These categorical variables are named:

   - **Early**: First fungicide application was prior to first sign of disease.

   - **Recommended**: First fungicide application was applied on the day powdery mildew was observed, or within three days of first sign.

   - **Late**: First fungicide application was four or more days after first sign of disease being observed.

@@

Single sprays of either:

   a) early,

   b) recommended timing,

   c) late.

Two or more sprays where the first spray was either:

   d) early,

   e) recommended timing,

   f) late.

@@

```{r simpler_clusters_remove}
slimmer_PM_dat <-
   slim_PM_dat[slim_PM_dat$spray_management != "Early_plus", ]
```

@@

```{r dose_lmer}
m1 <-
   lmer(log(grain_yield.t.ha * 1000) ~ factor(spray_management) +
           (1 | trial),
        data = slimmer_PM_dat)

@@

anova(m1, m2)
```

@@

```{r}
slimmer_PM_dat$trial <- slimmer_PM_dat$trial_noDose
slimmer_PM_dat <-
   slimmer_PM_dat[, colnames(slimmer_PM_dat) != "trial_noDose"] #remove second trial column
write.csv(slimmer_PM_dat, file = "cache/slimmer_PM_clusterdat.csv", row.names = FALSE)
```

@@

for (i in unique(slimmer_PM_dat$trial_ref)) {
   if (is.na(Trial_Dpress[Trial_Dpress$trial_ref == i, "AUDPC_C"])) {
      next()
   }

@@

   }
}
```

@@

We may want to consider row spacing in the trials, However one of the locations has `NA` as the row spacing. 
For now let's assign the most used row spacing of 0.33 m.

```{r assign_row_spacing_missing}
slimmer_PM_dat[is.na(slimmer_PM_dat$row_spacing),]
slimmer_PM_dat[is.na(slimmer_PM_dat$row_spacing),"row_spacing"] <- 0.33

@@
